---
title: "Barnacle upper limit surveys"
output:
  html_document: 
    keep_md: yes
  html_notebook: default
  pdf_document: default
---


Load packages
```{r warning=FALSE, error=FALSE}
library(dplyr)
library(ggplot2)
library(broom)
```


Read in data
```{r}
emersion <- read.csv("~/Documents/barnacle/emersion_time_upperlimits.csv")
emersion_noBoulder <- emersion %>% 
	filter(substrate != "boulder")

emersion_noBoulder <- emersion_noBoulder %>% 
	mutate(emersion_time_hours = ((total/60)/29))
```


Plot the upper limit in terms of height above MLLW
```{r}
emersion_noBoulder$Region <- ordered(emersion_noBoulder$Region, levels = c("gulf_islands", "vancouver", "outer_coast"))


emersion_noBoulder %>% 
ggplot(data = ., aes(x = Region, y = mean_height, fill = factor(substrate))) + geom_boxplot() + 
	ylab("height above MLLW, m") +
	theme(axis.text=element_text(size=16),
				axis.title=element_text(size=14,face="bold"))
```

Plot upper limit in terms of emersion time
```{r}
emersion_noBoulder %>% 
ggplot(data = ., aes(x = Region, y = emersion_time_hours, fill = factor(substrate))) + geom_boxplot() + 
	ylab("hours of emersion time per day") +
	theme(axis.text=element_text(size=16),
				axis.title=element_text(size=14,face="bold"))
```

Model fit of emersion hours as a function of substrate and region
```{r}
summary(lm(emersion_time_hours ~ substrate + Region, data = emersion_noBoulder))

```

Parameter estimates and confidence intervals for emersion_time_hours ~ substrate + Region
```{r}
emersion.fit <- tidy(lm(emersion_time_hours ~ substrate + Region, data = emersion_noBoulder), conf.int = TRUE)
knitr::kable(emersion.fit, align = 'c', format = 'markdown', digits = 2)
```

Model fit of height above MLLW as a function of substrate and region
```{r}
summary(lm(mean_height ~ substrate + Region, data = emersion_noBoulder))

```

Parameter estimates and confidence intervals for height above MLLW as a function of substrate and region
```{r}
emersion.fit <- tidy(lm(mean_height ~ substrate + Region, data = emersion_noBoulder), conf.int = TRUE)
knitr::kable(emersion.fit, align = 'c', format = 'markdown', digits = 2)
```

